---
title: 'Detailed Machine Learning Workflow Report'
author: "`r Sys.info()[['user']]`"
date: "`r date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(tools))
```

## ML Plan

Type: `r dataStore$mlPlan$type`

Target Variable: `r dataStore$mlPlan$target`

### Meta of Data

Number of classes: `r  dataStore$mlPlan$data.meta$number.of.classes`

Size of majority class: `r  dataStore$mlPlan$data.meta$majority.class.size`

Size of minority class: `r  dataStore$mlPlan$data.meta$minority.class.size`

Number of features: `r  dataStore$mlPlan$data.meta$number.of.features`

Number of numeric features: `r  dataStore$mlPlan$data.meta$number.of.numeric.features`

Number of symbolic features: `r  dataStore$mlPlan$data.meta$number.of.symbolic.features`

Number of records: `r  dataStore$mlPlan$data.meta$number.of.instances`

Number of records with missing values: `r  dataStore$mlPlan$data.meta$number.of.instances.with.missing.values`

Number of total missing values: `r  dataStore$mlPlan$data.meta$number.of.missing.values`


Data Highlight:
```{r echo=FALSE}

tibble::tibble(dataStore$mlPlan$data)

```

## ML Pipes
```{r echo=FALSE, comment=NA}

for (i in 1:length(dataStore$mlPlan$ml.pipelines)) {
    
    cat(paste('######################## ', dataStore$mlPlan$ml.pipelines[[i]]$id, ' ########################  \n',  sep = ''))
    cat('\n')
    
    dataStore$mlPlan$ml.pipelines[[i]]$printSelf()
    
}




```




## References

Thiloshon Nagarajah and Guhanathan Poravi (2019). automlr: Automated Machine Learning in R. R package version 0.0.009.
  
R Core Team (2012). R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria. ISBN 3-900051-07-0, URL http://www.R-project.org/


